\LARGE \bf Imposing a Weight Norm Constraint for Neuro–Adaptive Control

### 2025-03-31 manuscript.tex
minor update for jiyun

\author{Myeongseok Ryu$^{1}$, Jiyun Kim$^{2}$, and Kyunghwan Choi$^{3}$% <-this % stops a space
\thanks{
    *This work was supported in part by a Korea Research Institute for Defense Technology planning and advancement (KRIT) grant funded by Korea government DAPA (Defense Acquisition Program Administration) (No. KRIT-CT-22-087, Synthetic Battlefield Environment based Integrated Combat Training Platform) and in part by the National Research Foundation of Korea (NRF) grant funded by the Korea government (MSIT) (RS-2025-
00554087). \it{(Corresponding author: Kyunghwan Choi)}
}% <-this % stops a space
\thanks{
    $^{1}$Myeongseok Ryu is with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea {\tt\small dding\_98@gm.gist.ac.kr}
}%
\thanks{
    $^{2}$Jiyun Kim is with the Department of AI Convergence, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea 
        {\tt\small jiyun6606@gm.gist.ac.kr}
}%
\thanks{
    $^{3}$Kyunghwan Choi was with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, Republic of Korea. He is currently with the Graduate School of Mobility, Korea Advanced Institute of Science and Technology (KAIST), Daejeon 34051, Republic of Korea {\tt\small kyunghwan.choi90@gmail.com}
}%
}

>>>>

\author{Myeongseok Ryu$^{1}$, Jiyun Kim$^{2}$, and Kyunghwan Choi$^{3}$% <-this % stops a space
\thanks{
    *This work was supported in part by a Korea Research Institute for Defense Technology planning and advancement (KRIT) grant funded by Korea government DAPA (Defense Acquisition Program Administration) (No. KRIT-CT-22-087, Synthetic Battlefield Environment based Integrated Combat Training Platform) and in part by the National Research Foundation of Korea (NRF) grant funded by the Korea government (MSIT) (RS-2025-
00554087). \it{(Corresponding author: Kyunghwan Choi)}
}% <-this % stops a space
\thanks{
    $^{1}$Myeongseok Ryu is with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea {\tt\small dding\_98@gm.gist.ac.kr}
}%
\thanks{
    $^{2}$Jiyun Kim is with the AI Graduate School, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea {\tt\small jiyun6606@gm.gist.ac.kr}
}%
\thanks{
    $^{3}$Kyunghwan Choi was with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, Republic of Korea. He is currently with the Graduate School of Mobility, Korea Advanced Institute of Science and Technology (KAIST), Daejeon 34051, Republic of Korea {\tt\small kyunghwan.choi90@gmail.com}
}%
}
